{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}

### 2016-06-25 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
carry on

\begin{abstract}
Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns.
Defining the boundaries of urban regions is important to city planning, traffic management and resource allocation.
Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter regional activities.
In this study, we presented a method to redraw urban boundaries based upon human interaction with the physical space.
Specifically, we delineated the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million Twitter messages.
We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
The result of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas that provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
The technique was applied to both national scale (Great Britain) and municipal scale (the London metropolis). 
While our results corresponded well to the administrative boundaries, many unexpected and interesting boundaries were identified.

Our study connects human mobility research with the delineation of non-administrative anthropographic urban boundaries based on Twitter user spatial interactions, which provides a new understanding of the interactions between human activity and urban space.
\newline

>>>>

\begin{abstract}
Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns.
Defining the boundaries of urban regions is important to city planning, traffic management and resource allocation.
Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter regional activities.
In this study, we presented a method to redraw urban boundaries based upon human interaction with the physical space.
Specifically, we depicted the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million geo-located Twitter messages.
We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
The results of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas that provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
The technique was applied to both national scale (Great Britain) and municipal scale (the London metropolis).
While our results corresponded well to the administrative boundaries, many unexpected and interesting boundaries were identified.
More importantly, as the depicted urban boundaries exhibit a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to justify the distance decay effects in shaping the delineated urban boundaries.
The well fitted gravity model explains how the geographical distances found in the mobility pattern affecting the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
\newline
